---
title: "Spatial 2"
output: html_notebook
---

Conditional autoregression

Markov random field

$$
f(x_1),...,f(x_n) \overset{ind}{\sim} GP 
$$

1. Different type of fields we can generate
* negative correlation
* Jagged Gaussian
* Smooth Gaussian
* Other distributions
** Binomial start here
** Generalized Poisson
** Negative Binomial r=# of casts until r fish
2. Kansas tornado counts
3. Try many matern parameters
4. Different matern

particle filters
likelihood inference

$$
\rho(s,s^\prime) = \frac{C(s,s^\prime)}{\sqrt{C(s,s)C(s^\prime,s^\prime)}}
$$

```{r libraries, messages="FALSE"}
library(plgp) # distance
library(mvtnorm)
library(ggplot2)
library(viridis)
library(hrbrthemes)
library(Matrix)
```


$$
k_\nu(r)=\sigma^2\frac{2^{1-\nu}}{\Gamma(\nu)} \left(\frac{r}{\theta}\right)^{\nu} K_\nu \left(\frac{r}{\theta}\right)
$$


```{r matern covariance function}
matern = function(r, nu, theta, sig2=1) {
  result = sig2*(2^(1-nu))/gamma(nu) * (r/theta)^nu * besselK(r/theta, nu)
  result[is.nan(result)] = sig2
  return(result)
}
```


```{r Matern covariance 2D}
n = 40 # for 1000 x 1000 data requires 7500 GB memory
S = seq(-10,10,length=n)
SS = expand.grid(S,S) # All combinations of x,y coords
dist.SS = distance(SS)
```


```{r plot_nu}
for (nu in c(1/2, 2, 5)) {
  sig = matern(sqrt(dist.SS), nu, 1)
  samples = rmvnorm(1, rep(0,n^2), sig)
  transformed = t(qpois(pnorm(samples), 10))
  df = data.frame(cbind(SS, transformed))
  names(df) = c("X", "Y", "Counts")
  
  heat.map = ggplot() +
    geom_tile(data=df, aes(x=X, y=Y, fill=Counts)) +
    labs(title=paste("Poisson", "lambda=10"),
         subtitle=paste("40x40 Matern" ,"nu=", nu, "theta=1")) +
    scale_fill_viridis(option="magma", limits=c(0,25)) +
    theme_minimal()
  print(heat.map)
}

```


```{r plot_theta}
for (theta in c(2, 3, 6)) {
  sig = matern(sqrt(dist.SS), 2, theta, 1)
  samples = rmvnorm(1, rep(0,n^2), sig)
  transformed = t(qpois(pnorm(samples),10))
  df = data.frame(cbind(SS, transformed))
  names(df) = c("X", "Y", "Counts")
  
  heat.map = ggplot() +
    geom_tile(data=df, aes(x=X, y=Y, fill=Counts)) +
    labs(title=paste("Poisson", "lambda=10"),
         subtitle=paste("40x40 Matern", "nu=2", "theta=", theta)) +
    scale_fill_viridis(option="magma", limits=c(0,25)) +
    theme_minimal()
  print(heat.map)
}

```

# Generalized Poisson distribution

On accurate and precise generation of generalized Poisson variates
https://www-tandfonline-com.oca.ucsc.edu/doi/full/10.1080/03610918.2014.968725
$$
P_x(\theta,\lambda)=\frac{e^{-\theta-\lambda x}}{x!} \theta(\theta+\lambda x)^{x-1}
$$

$$
P[X_t=k] = \frac{e^{-(\lambda+\eta k)}}{k!} \lambda(\lambda+\eta k)^{k-1}
$$

```{r}
library(RNGforGPD)
```

```{r plot_gpois}
eta = 1/2
lambda = 10

for (nu in c(1/2, 2, 5)) {
  sig = matern(sqrt(dist.SS), nu, 1, 1)
  samples = rmvnorm(1, rep(0,n^2), sig)
  transformed = QuantileGpois(pnorm(samples), lambda, eta)
  df = data.frame(cbind(SS, transformed))
  names(df) = c("X", "Y", "Counts")
  
  heat.map = ggplot() +
    geom_tile(data=df, aes(x=X, y=Y, fill=Counts)) +
    labs(title=paste("Generalized Poisson", "lambda=",lambda, "eta=",eta),
         subtitle=paste("40x40 Matern" ,"nu=", nu, "theta=1")) +
    scale_fill_viridis(option="magma", limits=c(0,65)) +
    theme_minimal()
  print(heat.map)
}
```

```{r plot_nbinom}
p = 1/2
N = 30

for (nu in c(1/2, 2, 5)) {
  sig = matern(sqrt(dist.SS), nu, 1, 1)
  samples = rmvnorm(1, rep(0,n^2), sig)
  transformed = t(qnbinom(pnorm(samples), N, p))
  df = data.frame(cbind(SS, transformed))
  names(df) = c("X", "Y", "Counts")
  
  heat.map = ggplot() +
    geom_tile(data=df, aes(x=X, y=Y, fill=Counts)) +
    labs(title=paste("Negative Binomial", "N=", N, "p=", p),
         subtitle="40x40 Matern", "nu=", nu, "theta=1") +
    scale_fill_viridis(option="magma", limits=c(0,65)) +
    theme_minimal()
  print(heat.map)
}
```