---
title: "Spatial"
output: html_notebook
---

# Correlated joint Poisson distribution

A copula is a distribution function on the n-dimensional unit cuve with uniformly distributed margins. (Kazianka-Pilz2010)

Suppose we have 4 stations denoted by

$$
S = 
\begin{pmatrix}
s_1 \\ s_2 \\ s_3 \\ s_4
\end{pmatrix}
$$

and

$$
Z(s) \sim GP(0,R_{4\times 4})
$$

Let $\Phi$ be the CDF of N(0,1) RV, Then

$$
(U_1, U_2, U_3, U_4) = \left(\Phi(Z(s_1)),\Phi(Z(s_2)),\Phi(Z(s_3)),\Phi(Z(s_4))\right)
$$
Denote F as the CDF of a Poisson($\lambda$) distribution. Set

$$
X(s) = F^{-1}[\Phi(Z(s))]
$$
where
$$
F^{-1}(U) = \inf \{x:F(x) \geq U\}
$$

$$
(X(s_1),X(s_2),X(s_3),X(s_4)) \overset{D}{\sim} \text{Poisson}(\lambda)
$$
with correlation


Goal: To generate Poisson random fields, and plot the results

$$
\begin{aligned}
\{Z(s) = Z(s_1),Z(s_2),...,Z(s_N)\} && N \text{ locations } 1,...,N 
\end{aligned}
$$
$Z$ must be a standard normal

If we have a MVN RV 

$$Y \sim N_N(\mu,\Sigma)$$

we can write it as

$$
Y = \mu + \Sigma^{1/2}W
$$

where

$$
W = N_N(0,I_{N\times N})
$$

## 1D

```{r libraries, messages="FALSE"}
library(plgp) # distance
library(mvtnorm)
library(ggplot2)
library(viridis)
library(hrbrthemes)
```


```{r covariance functions}
# squared distances as input
squared.exponential = function(r, l) {
  eps = sqrt(.Machine$double.eps)
  if (is.null(dim(r))==FALSE) {
    n = dim(r)[1]
    exp(-r/(2*l)) + diag(eps, n)
  } else {
    exp(-r/(2*l))
  }
}

matern = function(r, nu, theta) {
  result = (2^(1-nu))/gamma(nu) * (r*sqrt(2*nu/theta))^nu * besselK(r*sqrt(2*nu/theta), nu)
  result[is.nan(result)] = 1
  return(result)
}
```

```{r myMVN function}
myMVN = function(n, mu, Sigma) {
  if (length(mu) != dim(Sigma)[1]) stop("Mean and covariance matrix have non-conforming size")
  d = dim(Sigma)[1]
  samples = matrix(rnorm(d*n, 0, 1), nrow=d, ncol=n)
  chol.Sigma = t(chol(Sigma)) # chol returns upper triangular
  t(mu + chol.Sigma %*% samples)
}
```

```{r data}
# 200 points from -10 to 10 (1D)
n = 200
S = matrix(seq(-10,10,length=n), ncol=1)
D = distance(S) # returns squared distances
sigma.exp1D = squared.exponential(D,1)
sigma.mat1D = matern(sqrt(D), 2, 1)
```

```{r differences}
# Builtin
plot(S,rmvnorm(1, rep(0,200), sigma.exp1D), type="l", ylim=c(-10,10),
     main="rmvnorm (from library)")
for (i in 1:20) {
  builtin.samples = rmvnorm(1, rep(0,200), sigma.exp1D)
  lines(S, builtin.samples, col="gray")
}

# From scratch
plot(S,myMVN(1, rep(0,200), sigma.exp1D), type="l", ylim=c(-10,10),
     main="myMVN (from scratch)")
for (i in 1:20) {
  mySamples = myMVN(1, rep(0,200), sigma.exp1D)
  lines(S, mySamples, col="gray")
}

```

MVN from scratch looks to perform similarly to the one from the library. However, the one from the library can handle covariance matrices better


```{r}
n = 200
S = matrix(seq(-10,10,length=n), ncol=1)
D = distance(S) # returns squared distances
sigma.exp1D = squared.exponential(D,1)
sigma.mat1D = matern(sqrt(D), 2, 1) # nu = 2, theta=1

normsamples.exp1D = myMVN(1, rep(0,n), sigma.exp1D)
normsamples.mat1D = myMVN(1, rep(0,n), sigma.mat1D)

plot(S, normsamples.exp1D, type="l",
     main="Exponential Covariance matrix")
plot(S, normsamples.mat1D, type="l",
     main="Matern Covariance matrix")

transformed.exp1D = qpois(pnorm(myMVN(1, rep(0,n), sigma.exp1D)), 10)
transformed.mat1D = qpois(pnorm(myMVN(1, rep(0,n), sigma.mat1D)), 10)
plot(S, transformed.exp1D,
     main="Exponential Covariance matrix")
plot(S, transformed.mat1D,
     main="Matern Covariance matrix")
```


## 2D

```{r Exponential covariance 2D}
n = 30
S = seq(-10,10,length=n)
SS = expand.grid(S,S) # All combinations of x,y coords
dist.SS = distance(SS)
sigma.2D = squared.exponential(dist.SS,1)

samples.2D = myMVN(1, rep(0,n^2), sigma.2D)
transformed.2D = t(qpois(pnorm(samples.2D),10))

df.2D = data.frame(cbind(SS, transformed.2D))
names(df.2D) = c("X", "Y", "Counts")

heat.2D = ggplot() +
  geom_tile(data=df.2D, aes(x=X, y=Y, fill=Counts)) +
  labs(title="Exponential") +
  scale_fill_viridis(option="magma") +
  theme_minimal()
heat.2D

# persp(S,S, qpois(pnorm(matrix(samples.2D, ncol=50)),1), theta=30, phi=30)
```

```{r Matern covariance 2D}
n = 30
S = seq(-10,10,length=n)
SS = expand.grid(S,S) # All combinations of x,y coords
dist.SS = distance(SS)
sigma.matern = matern(sqrt(dist.SS), 2, 1)
samples.matern = myMVN(1, rep(0,n^2), sigma.matern)
transformed.matern = t(qpois(pnorm(samples.matern),10))
df.matern = data.frame(cbind(SS, transformed.matern))
names(df.matern) = c("X", "Y", "Counts")

heat.matern = ggplot() +
  geom_tile(data=df.matern, aes(x=X, y=Y, fill=Counts)) +
  labs(title="Matern") +
  scale_fill_viridis(option="magma") +
  theme_minimal()
heat.matern
```

```{r}
par(pty="s")
empirical = sort(transformed.matern)
theoretical = qpois((1:900)/901,10)
plot(theoretical, empirical, xlim=c(0,20), ylim=c(0,20))
lines(stepfun(1:900,0:900), col="red", do.points=F)
abline(c(0,1))
```


```{r}
library(fitdistrplus)
plot(fitdist(as.vector(transformed.matern),"pois"))
```

